Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-09 doc/paper.tex
finishes first draft of results

% \subsection{Evaluation Metrics}
% \label{sec:results:metrics}
% \dots

@@

\subsection{Pre-training on Out-of-Distribution data}
\label{sec:results:varying}

@@

When using point correspondences without overlapping scans, the performance gain disappears almost entirely. This was noted in their original work and suggests to us that it is learning better features only due to its ability to better extrapolate surfaces.

@@

The performance gains are unpredictable as the fraction of labeled data is varied. A performance boost of 3\% at 30\% labeled data can turn into a performance drop at 20\% labeled data. At the extreme of using 5\% labeled data, all algorithms have a performance boost. This further reinforces the idea that pre-training is most useful when the amount of labeled data is extremely limited. Interestingly, DepthContrast which was the worst performing on S3DIS is the best performing by a large margin on Scannet at 5\% labeled data, again showing the unpredictability of the results.

@@

@@

>>>>

@@

\subsection{Pre-training on Out-of-Distribution data}
\label{sec:results:out-of-distribution}

@@

In table \ref{table:scannetVaryingDataAmount}, the performance gains are unpredictable as the fraction of labeled data is varied. A performance boost of 3\% at 30\% labeled data can turn into a performance drop at 20\% labeled data. At the extreme of using 5\% labeled data, all algorithms have a performance boost. This further reinforces the idea that pre-training is most useful when the amount of labeled data is extremely limited. Interestingly, DepthContrast which was the worst performing on S3DIS is the best performing by a large margin on Scannet at 5\% labeled data, again showing the unpredictability of the results.

@@

@@

In this work, we presented a method of transferring self-supervised features derived from dense images to models working on sparse point clouds. We showed how these features performed on three different downstream tasks and three different datasets. We also compared our approach to other methods.

We found that our method was relatively consistent at improving downstream performance when compared to state of the art, with around a 1\% increase in performance on average. On larger datasets, using all labeled data for pre-training and training showed no performance increase, however when pre-trained on another dataset, performance did improve.

It is very hard to tell which weights will perform best on which downstream task. From our experiments we found that using images had a benefit much more often than methods that used only point clouds. Since it works on raw captured 3D data, it is also easier to implement than those on registered point clouds. When looking for pre-training weights, our method is the best starting point to see if it can improve on a specific downstream task.

Across all methods, using different datasets for pre-training than for training offered a bigger performance boost than using the same dataset. However, it the effects are still very inconsistent across domains.

When starting to work on a problem, it may be worth while to try a self-supervised technique on a smaller labeled dataset before labeling it entirely. It can also be used to improve development iterations as it achieves close to final performance in a fraction of the training steps.

@@

\section{Conclusion}
